---
title: "Basis Analysis of Hurricane Florence"
output: html_document
params:
  only_nc_sc: TRUE
---

```{r setup, include=FALSE}
options(width = 100)
```

```{r echo=FALSE, include=FALSE}
library(readr)
pre_florence  <- read_csv("Data/pre-processed pre florence.csv")
post_florence <- read_csv("Data/pre-processed post florence.csv")
both_florence <- read_csv("Data/pre-processed both pre post florence.csv")
```

### Sample size

```{r}
dim(pre_florence)[1]
```
```{r}
dim(post_florence)[1]
```
```{r}
dim(both_florence)[1]
```

## inclusion/exclusion cretiria
#### Only NC or SC
```{r}
table(pre_florence$state)
table(post_florence$state)

if(params$only_nc_sc)
{
  pre_florence <- pre_florence[which(pre_florence$state == "NC" | pre_florence$state == "SC"),]
  post_florence <- post_florence[which(post_florence$state == "NC" | post_florence$state == "SC"),]
}

```

### Sample size after exclusion

```{r}
dim(pre_florence)[1]
```
```{r}
dim(post_florence)[1]
```

```{r echo=FALSE, include=FALSE}
## Organize order of factor
gender_order <- c("Female","Male","Other")
pre_florence$gender  <- factor(pre_florence$gender, levels=gender_order)
post_florence$gender <- factor(post_florence$gender, levels=gender_order)
both_florence$pre_gender <- factor(both_florence$pre_gender, levels=gender_order)
both_florence$post_gender <- factor(both_florence$post_gender, levels=gender_order)

edu_order <- c("Some high school","High school graduate",
               "Some college","College graduate","Graduate school")
pre_florence$edu  <- factor(pre_florence$edu, levels=edu_order)
post_florence$edu <- factor(post_florence$edu, levels=edu_order)
both_florence$pre_edu <- factor(both_florence$pre_edu, levels=edu_order)
both_florence$post_edu <- factor(both_florence$post_edu, levels=edu_order)

income_order <- c("Less than $20,000","$20,000 to $40,000","$40,000 to $60,000",
                  "$60,000 to $80,000","$80,000 to $100,000","$100,000 to $150,000",
                  "Over $150,000")
pre_florence$income  <- factor(pre_florence$income, levels=income_order)
post_florence$income <- factor(post_florence$income, levels=income_order)
both_florence$pre_income <- factor(both_florence$pre_income, levels=income_order)
both_florence$post_income <- factor(both_florence$post_income, levels=income_order)

years_in_res_order <- c("Less than 1 year","1  - 3 years","3 - 5 years",
                        "5 - 10 years","More than 10 years")
pre_florence$years_in_resident  <- factor(pre_florence$years_in_resident, levels=years_in_res_order)
post_florence$years_in_resident <- factor(post_florence$years_in_resident, levels=years_in_res_order)
both_florence$pre_years_in_resident <- factor(both_florence$pre_years_in_resident, levels=years_in_res_order)
both_florence$post_years_in_resident <- factor(both_florence$post_years_in_resident, levels=years_in_res_order)

distance_order <- c("Within 1 mile","1 to 4 miles","4 to 10 miles",
                   "10 to 30 miles","30 to 50 miles","More than 50 miles")
pre_florence$distance_to_coast  <- factor(pre_florence$distance_to_coast, levels=distance_order)
post_florence$distance_to_coast <- factor(post_florence$distance_to_coast, levels=distance_order)
both_florence$pre_distance_to_coast <- factor(both_florence$pre_distance_to_coast, levels=distance_order)
both_florence$post_distance_to_coast <- factor(both_florence$post_distance_to_coast, levels=distance_order)

house_order <- c("Mobile or  trailer home","Detached single family house","Duplex or triplex house","Condominium/apartment","Other")
pre_florence$house_structure  <- factor(pre_florence$house_structure, levels=house_order)
post_florence$house_structure <- factor(post_florence$house_structure, levels=house_order)

num_vehicle_order <- c("None","One","More than one")
pre_florence$num_vehicle  <- factor(pre_florence$num_vehicle, levels=num_vehicle_order)
post_florence$num_vehicle <- factor(post_florence$num_vehicle, levels=num_vehicle_order)
both_florence$pre_num_vehicle <- factor(both_florence$pre_num_vehicle, levels=num_vehicle_order)
both_florence$post_num_vehicle <- factor(both_florence$post_num_vehicle, levels=num_vehicle_order)

important_order <- c("Extremely important","Very important","Moderately important","Slightly important","Not at all important")
pre_florence$importance_of_pet  <- factor(pre_florence$importance_of_pet, levels=important_order)
post_florence$importance_of_pet <- factor(post_florence$importance_of_pet, levels=important_order)
both_florence$pre_importance_of_pet <- factor(both_florence$pre_importance_of_pet, levels=important_order)
both_florence$post_importance_of_pet <- factor(both_florence$post_importance_of_pet, levels=important_order)

amount_order <- c("None at all","A little","A moderate amount","A lot","A great deal")

## social influence
#### pre
pre_florence$contribute_final_decision <- factor(pre_florence$contribute_final_decision, levels=amount_order)
pre_florence$household_discussion      <- factor(pre_florence$household_discussion, levels=amount_order)
pre_florence$household_influence       <- factor(pre_florence$household_influence, levels=amount_order)
pre_florence$outside_family_discussion <- factor(pre_florence$outside_family_discussion, levels=amount_order)
pre_florence$outside_family_influence  <- factor(pre_florence$outside_family_influence, levels=amount_order)
pre_florence$outside_friend_discussion <- factor(pre_florence$outside_friend_discussion, levels=amount_order)
pre_florence$outside_friend_influence  <- factor(pre_florence$outside_friend_influence, levels=amount_order)
pre_florence$neighbors_influence       <- factor(pre_florence$neighbors_influence, levels=amount_order)
pre_florence$neighbors_observation     <- factor(pre_florence$neighbors_observation, levels=amount_order)
#### post
post_florence$contribute_final_decision <- factor(post_florence$contribute_final_decision, levels=amount_order)
post_florence$household_discussion      <- factor(post_florence$household_discussion, levels=amount_order)
post_florence$outside_family_discussion <- factor(post_florence$outside_family_discussion, levels=amount_order)
post_florence$outside_friend_discussion <- factor(post_florence$outside_friend_discussion, levels=amount_order)
post_florence$neighbors_observation     <- factor(post_florence$neighbors_observation, levels=amount_order)
#### both
both_florence$contribute_final_decision <- factor(both_florence$pre_contribute_final_decision, levels=amount_order)
both_florence$household_discussion      <- factor(both_florence$pre_household_discussion, levels=amount_order)
both_florence$household_influence       <- factor(both_florence$pre_household_influence, levels=amount_order)
both_florence$outside_family_discussion <- factor(both_florence$pre_outside_family_discussion, levels=amount_order)
both_florence$outside_family_influence  <- factor(both_florence$pre_outside_family_influence, levels=amount_order)
both_florence$outside_friend_discussion <- factor(both_florence$pre_outside_friend_discussion, levels=amount_order)
both_florence$outside_friend_influence  <- factor(both_florence$pre_outside_friend_influence, levels=amount_order)
both_florence$neighbors_influence       <- factor(both_florence$pre_neighbors_influence, levels=amount_order)
both_florence$neighbors_observation     <- factor(both_florence$pre_neighbors_observation, levels=amount_order)
both_florence$contribute_final_decision <- factor(both_florence$post_contribute_final_decision, levels=amount_order)
both_florence$household_discussion      <- factor(both_florence$post_household_discussion, levels=amount_order)
both_florence$outside_family_discussion <- factor(both_florence$post_outside_family_discussion, levels=amount_order)
both_florence$outside_friend_discussion <- factor(both_florence$post_outside_friend_discussion, levels=amount_order)
both_florence$neighbors_observation     <- factor(both_florence$post_neighbors_observation, levels=amount_order)

## infomation
#### pre
pre_florence$TVR_causualities   <- factor(pre_florence$TVR_causualities, levels= amount_order)
pre_florence$TVR_dmg_done       <- factor(pre_florence$TVR_dmg_done, levels= amount_order)
pre_florence$TVR_evac           <- factor(pre_florence$TVR_evac, levels= amount_order)
pre_florence$TVR_forecasted_dmg <- factor(pre_florence$TVR_forecasted_dmg, levels= amount_order)
pre_florence$TVR_preparing      <- factor(pre_florence$TVR_preparing, levels= amount_order)
pre_florence$TVR_stay           <- factor(pre_florence$TVR_stay, levels= amount_order)
pre_florence$TVR_traffic_jams   <- factor(pre_florence$TVR_traffic_jams, levels= amount_order)
pre_florence$SM_causualities    <- factor(pre_florence$SM_causualities, levels= amount_order)
pre_florence$SM_dmg_done        <- factor(pre_florence$SM_dmg_done, levels= amount_order)
pre_florence$SM_evac            <- factor(pre_florence$SM_evac, levels= amount_order)
pre_florence$SM_forecasted_dmg  <- factor(pre_florence$SM_forecasted_dmg, levels= amount_order)
pre_florence$SM_preparing       <- factor(pre_florence$SM_preparing, levels= amount_order)
pre_florence$SM_stay            <- factor(pre_florence$SM_stay, levels= amount_order)
pre_florence$SM_traffic_jams    <- factor(pre_florence$SM_traffic_jams, levels= amount_order)
#### post
post_florence$TVR_causualities   <- factor(post_florence$TVR_causualities, levels= amount_order)
post_florence$TVR_dmg_done       <- factor(post_florence$TVR_dmg_done, levels= amount_order)
post_florence$TVR_evac           <- factor(post_florence$TVR_evac, levels= amount_order)
post_florence$TVR_forecasted_dmg <- factor(post_florence$TVR_forecasted_dmg, levels= amount_order)
post_florence$TVR_preparing      <- factor(post_florence$TVR_preparing, levels= amount_order)
post_florence$TVR_stay           <- factor(post_florence$TVR_stay, levels= amount_order)
post_florence$TVR_traffic_jams   <- factor(post_florence$TVR_traffic_jams, levels= amount_order)
post_florence$SM_causualities    <- factor(post_florence$SM_causualities, levels= amount_order)
post_florence$SM_dmg_done        <- factor(post_florence$SM_dmg_done, levels= amount_order)
post_florence$SM_evac            <- factor(post_florence$SM_evac, levels= amount_order)
post_florence$SM_forecasted_dmg  <- factor(post_florence$SM_forecasted_dmg, levels= amount_order)
post_florence$SM_preparing       <- factor(post_florence$SM_preparing, levels= amount_order)
post_florence$SM_stay            <- factor(post_florence$SM_stay, levels= amount_order)
post_florence$SM_traffic_jams    <- factor(post_florence$SM_traffic_jams, levels= amount_order)
#### both
both_florence$pre_TVR_causualities   <- factor(both_florence$pre_TVR_causualities, levels= amount_order)
both_florence$pre_TVR_dmg_done       <- factor(both_florence$pre_TVR_dmg_done, levels= amount_order)
both_florence$pre_TVR_evac           <- factor(both_florence$pre_TVR_evac, levels= amount_order)
both_florence$pre_TVR_forecasted_dmg <- factor(both_florence$pre_TVR_forecasted_dmg, levels= amount_order)
both_florence$pre_TVR_preparing      <- factor(both_florence$pre_TVR_preparing, levels= amount_order)
both_florence$pre_TVR_stay           <- factor(both_florence$pre_TVR_stay, levels= amount_order)
both_florence$pre_TVR_traffic_jams   <- factor(both_florence$pre_TVR_traffic_jams, levels= amount_order)
both_florence$pre_SM_causualities    <- factor(both_florence$pre_SM_causualities, levels= amount_order)
both_florence$pre_SM_dmg_done        <- factor(both_florence$pre_SM_dmg_done, levels= amount_order)
both_florence$pre_SM_evac            <- factor(both_florence$pre_SM_evac, levels= amount_order)
both_florence$pre_SM_forecasted_dmg  <- factor(both_florence$pre_SM_forecasted_dmg, levels= amount_order)
both_florence$pre_SM_preparing       <- factor(both_florence$pre_SM_preparing, levels= amount_order)
both_florence$pre_SM_stay            <- factor(both_florence$pre_SM_stay, levels= amount_order)
both_florence$pre_SM_traffic_jams    <- factor(both_florence$pre_SM_traffic_jams, levels= amount_order)
both_florence$post_TVR_causualities   <- factor(both_florence$post_TVR_causualities, levels= amount_order)
both_florence$post_TVR_dmg_done       <- factor(both_florence$post_TVR_dmg_done, levels= amount_order)
both_florence$post_TVR_evac           <- factor(both_florence$post_TVR_evac, levels= amount_order)
both_florence$post_TVR_forecasted_dmg <- factor(both_florence$post_TVR_forecasted_dmg, levels= amount_order)
both_florence$post_TVR_preparing      <- factor(both_florence$post_TVR_preparing, levels= amount_order)
both_florence$post_TVR_stay           <- factor(both_florence$post_TVR_stay, levels= amount_order)
both_florence$post_TVR_traffic_jams   <- factor(both_florence$post_TVR_traffic_jams, levels= amount_order)
both_florence$post_SM_causualities    <- factor(both_florence$post_SM_causualities, levels= amount_order)
both_florence$post_SM_dmg_done        <- factor(both_florence$post_SM_dmg_done, levels= amount_order)
both_florence$post_SM_evac            <- factor(both_florence$post_SM_evac, levels= amount_order)
both_florence$post_SM_forecasted_dmg  <- factor(both_florence$post_SM_forecasted_dmg, levels= amount_order)
both_florence$post_SM_preparing       <- factor(both_florence$post_SM_preparing, levels= amount_order)
both_florence$post_SM_stay            <- factor(both_florence$post_SM_stay, levels= amount_order)
both_florence$post_SM_traffic_jams    <- factor(both_florence$post_SM_traffic_jams, levels= amount_order)

prob_order <- c("Extremely unlikely","Moderately unlikely","Slightly unlikely","Neither likely nor unlikely (50/50)","Slightly likely","Moderately likely","Extremely likely")
## pre 
pre_florence$evac_prob     <- factor(pre_florence$evac_prob, levels=prob_order)
pre_florence$safety_prob   <- factor(pre_florence$safety_prob, levels=prob_order)
pre_florence$supplier_prob <- factor(pre_florence$supplier_prob, levels=prob_order)
pre_florence$job_lost_prob <- factor(pre_florence$job_lost_prob, levels=prob_order)
## post
post_florence$safety_prob <- factor(post_florence$safety_prob, levels=prob_order)
## both
both_florence$pre_evac_prob <- factor(both_florence$pre_evac_prob, levels=prob_order)
both_florence$pre_safety_prob   <- factor(both_florence$pre_safety_prob, levels=prob_order)
both_florence$pre_supplier_prob <- factor(both_florence$pre_supplier_prob, levels=prob_order)
both_florence$pre_job_lost_prob <- factor(both_florence$pre_job_lost_prob, levels=prob_order)
both_florence$post_safety_prob <- factor(both_florence$post_safety_prob, levels=prob_order)

flood_depth_order <- c("Will not be flooded","1 foot or less","2 - 3 feet","4 - 5 feet",
                       "More than 5 feet")
pre_florence$flood_depth <- factor(pre_florence$flood_depth, levels=flood_depth_order)
post_florence$flood_depth <- factor(post_florence$flood_depth, levels=flood_depth_order)
both_florence$pre_flood_depth <- factor(both_florence$pre_flood_depth, levels=flood_depth_order)
both_florence$post_flood_depth <- factor(both_florence$post_flood_depth, levels=flood_depth_order)

electricity_dur_order <- c("Will not lose electricity","Less than one week","1 - 2 weeks","3 - 4 weeks","More than a month")
pre_florence$electricity_lost_dur <- factor(pre_florence$electricity_lost_dur, levels=electricity_dur_order)
post_florence$electricity_lost_dur <- factor(post_florence$electricity_lost_dur, levels=electricity_dur_order)
both_florence$electricity_lost_dur <- factor(both_florence$pre_electricity_lost_dur, levels=electricity_dur_order)
both_florence$electricity_lost_dur <- factor(both_florence$post_electricity_lost_dur, levels=electricity_dur_order)

normal_cond_order <- c("Less than one week","1 - 2 weeks","3 -4 weeks","More than a month")
pre_florence$normal_condition_return <- factor(pre_florence$normal_condition_return, levels=normal_cond_order)
post_florence$normal_condition_return <- factor(post_florence$normal_condition_return, levels=normal_cond_order)
both_florence$normal_condition_return <- factor(both_florence$pre_normal_condition_return, levels=normal_cond_order)
both_florence$normal_condition_return <- factor(both_florence$post_normal_condition_return, levels=normal_cond_order)


agree_order <- c("Fully disagree","Somewhat disagree","Neither agree nor disagree","Somewhat agree","Fully agree")
post_florence$household_agreement <- factor(post_florence$household_agreement, levels=agree_order)
post_florence$outside_family_agreement <- factor(post_florence$outside_family_agreement, levels=agree_order)
post_florence$outside_friend_agreement <- factor(post_florence$outside_friend_agreement, levels=agree_order)
post_florence$neighbors_agreement <- factor(post_florence$neighbors_agreement, levels=agree_order)

both_florence$post_household_agreement <- factor(both_florence$post_household_agreement, levels=agree_order)
both_florence$post_outside_family_agreement <- factor(both_florence$post_outside_family_agreement, levels=agree_order)
both_florence$post_outside_friend_agreement <- factor(both_florence$post_outside_friend_agreement, levels=agree_order)
both_florence$post_neighbors_agreement <- factor(both_florence$post_neighbors_agreement, levels=agree_order)

## notice type factor
pre_florence$mandatory_evac_notice <- factor(pre_florence$mandatory_evac_notice)
pre_florence$voluntary_evac_notice <- factor(pre_florence$voluntary_evac_notice)
pre_florence$voluntary_stay_notice <- factor(pre_florence$voluntary_stay_notice)
pre_florence$mandatory_stay_notice <- factor(pre_florence$mandatory_stay_notice)

post_florence$mandatory_evac_notice <- factor(post_florence$mandatory_evac_notice)
post_florence$voluntary_evac_notice <- factor(post_florence$voluntary_evac_notice)
post_florence$voluntary_stay_notice <- factor(post_florence$voluntary_stay_notice)
post_florence$mandatory_stay_notice <- factor(post_florence$mandatory_stay_notice)

## Date ordering
when_first_hear_order <- c("September 6th or before","September 7th","September 8th",
                           "September 9th","September 10th")
pre_florence$when_first_hear <- factor(pre_florence$when_first_hear, levels = when_first_hear_order)

when_prepare_stay_order <- c("September 6th or before","September 7th","September 8th",
                       "September 9th","September 10th","September 11th","September 12th")
post_florence$when_prepare_stay <- factor(post_florence$when_prepare_stay, 
                                          levels = when_prepare_stay_order)
notice_when_order <- c("September 6th or before","September 7th","September 8th",
                       "September 9th","September 10th","September 11th",
                       "September 12th","September 13th","September 14th",
                       "September 15th or after")
post_florence$notice_when <- factor(post_florence$notice_when, levels=notice_when_order)
date_evac_order <- c("September 6th or before","September 7th","September 8th",
                       "September 9th","September 10th","September 11th",
                       "September 12th","September 13th","September 14th","September 15th or after")
post_florence$date_evac <- factor(post_florence$date_evac, levels=date_evac_order)

## Other don't care about order but need to translate it to factor for summarization purpose
all_character_class_pre <- names(pre_florence[,sapply(pre_florence,is.character)])
for(name in all_character_class_pre)
{
  pre_florence[[name]] <- as.factor(pre_florence[[name]])
}

all_character_class_post <- names(post_florence[,sapply(post_florence,is.character)])
for(name in all_character_class_post)
{
  post_florence[[name]] <- as.factor(post_florence[[name]])
}
all_character_class_both <- names(both_florence[,sapply(both_florence,is.character)])
for(name in all_character_class_both)
{
  both_florence[[name]] <- as.factor(both_florence[[name]])
}

```

# Standard summarization in text 

## Demographical Infomation
#### Pre

```{r}
summary(pre_florence[5:25])
```

#### Post

```{r}
summary(post_florence[5:25])
```

## Social influence
#### pre

```{r}
summary(pre_florence[26:34])
```

#### post

```{r}
summary(post_florence[26:34])
```

## Prev experience
#### pre

```{r}
summary(pre_florence[35:43])
```

#### post

```{r}
summary(post_florence[35:40])
```

## Probability and Estimation
#### pre

```{r}
summary(pre_florence[44:57])
```

#### post

```{r}
summary(post_florence[41:46])
```

## Infomation
#### pre

```{r}
summary(pre_florence[58:73])
```

#### post

```{r}
summary(post_florence[47:62])
```

## Pre specific Question
#### First hear

```{r}
summary(pre_florence[74:82])
```

## Post specific Question
#### First hear, Official Notice, emergency request and decision

```{r}
summary(post_florence[63:71])
```

#### Evac specific question

```{r}
summary(post_florence[72:78])
```

#### Stay specific question

```{r}
summary(post_florence[79:83])
```

#### Notice type specific question

```{r}
summary(post_florence[84:88])
```

#### Correlation Table

```{r echo=FALSE}
y_list <- c(#"flood_cost","electricity_cost",
            "traveling_cost","safe_place_cost","safety_prob",
            "flood_depth","electricity_lost_dur","normal_condition_return","evac_decision_num")

x_list <- c("age","gender","edu","income","house_structure","years_in_resident","distance_to_coast","num_vehicle",
            "has_pet","family_size","child_0_5","child_6_12","child_13_18","elder_65_up",
             "special_need_med","special_need_moving",
             "mandatory_evac_notice","voluntary_evac_notice","prev_exp_decision",
            #"flood_cost","electricity_cost",
            "traveling_cost","safe_place_cost","safety_prob",
            "flood_depth","electricity_lost_dur","normal_condition_return")
## Clearning up some features
pre_florence$evac_decision_num <- as.numeric(pre_florence$evac_prob)
post_florence$evac_decision_num <- as.numeric(post_florence$evac_decision)
pre_florence$prev_exp_decision <- ifelse(pre_florence$prev_exp == "No",0, ifelse(pre_florence$prev_exp_decision == "Evacuated",1,2))
post_florence$prev_exp_decision <- ifelse(post_florence$prev_exp == "No",0, ifelse(post_florence$prev_exp_decision == "Evacuated",1,2))
pre_florence <- pre_florence[which(pre_florence$heard_florence == "Yes"),]

post_florence$traveling_cost <- ifelse(post_florence$evac_decision == "No", post_florence$traveling_est_stay, post_florence$traveling_cost_evac)
post_florence$safe_place_cost <- ifelse(post_florence$evac_decision == "No", post_florence$place_cost_est_stay, post_florence$place_cost_evac)

dat <- pre_florence 
dat <- post_florence

for(x in x_list)
{
  temp <- ""
  for(y in y_list)
  {
    cor_temp <- round(cor(as.numeric(dat[[x]]),as.numeric(dat[[y]])),digits=2)
    temp <- paste(temp,cor_temp, sep=" & ")
  }
  print(temp)
}

```

```{r echo=FALSE}
## helper function for ploting
gen_bar_plot <- function(dat,plot_list)
{
  for(i in plot_list)
  {
    barplot(table(dat[[i]]),ylab="Number of response",xlab=i)
  }
}
gen_box_plot <- function(dat,plot_list,maxy)
{
  for(i in plot_list)
  {
    boxplot(dat[[i]],ylab="value (count or cost)",xlab=i,ylim=c(0,maxy))
  }
}

```

## Pre Hurricane Florence
### Ploting demographical information 

```{r echo=FALSE}
## Standard Summarization of Categorical variables in barplot
category_to_plot <- c("gender","num_vehicle","has_pet",
                      "child_0_5","child_6_12","child_13_18","elder_65_up",
                      "special_need_med","special_need_moving")
gen_bar_plot(pre_florence,category_to_plot)
```
```{r echo=FALSE, fig.width=15}
category_to_plot <- c("edu","income","house_structure","years_in_resident",
                      "distance_to_coast")
gen_bar_plot(pre_florence,category_to_plot)
```
```{r echo=FALSE}
## Standard summarization of numerical variables in boxplot
numerical_to_plot <- c("family_size")
gen_box_plot(pre_florence,numerical_to_plot,15)
```

### Ploing social influence

```{r echo=FALSE, fig.width=10}
#### list of things to plot
category_to_plot <- c("contribute_final_decision","household_discussion","household_influence",
                      "outside_family_discussion","outside_family_influence",
                      "outside_friend_discussion","outside_friend_influence",
                      "neighbors_observation","neighbors_influence")
gen_bar_plot(pre_florence,category_to_plot)
```

### Ploting previous experience

```{r echo=FALSE, fig.width=12}
#### list of things to plot
category_to_plot <- c("place_to_evac","how_to_evac")
gen_bar_plot(pre_florence,category_to_plot)
```
```{r echo=FALSE}
#### list of things to plot
category_to_plot <- c("prev_exp","prev_exp_decision")
gen_bar_plot(pre_florence,category_to_plot)
```

### Ploting probability estimation 

```{r echo=FALSE, fig.width=14}
#### list of things to plot
category_to_plot <- c("evac_prob","safety_prob","supplier_prob","job_lost_prob",
                      "flood_depth","electricity_lost_dur","normal_condition_return",
                      "hurricane_category")
gen_bar_plot(pre_florence,category_to_plot)
```

### Ploting utility equivalent and cost estimation

```{r echo=FALSE}
#### list of things to plot
numerical_to_plot <- c("flood_cost","electricity_cost","shelter_cost",
                       "traveling_cost","safe_place_cost")
gen_box_plot(pre_florence,numerical_to_plot,3000)
```
```{r echo=FALSE}
#### list of things to plot
numerical_to_plot <- c("damage_est")
gen_box_plot(pre_florence,numerical_to_plot,50000)
```

### Ploting information

```{r echo=FALSE, fig.width=10}
#### list of things to plot
category_to_plot <- c("TVR_dmg_done","TVR_forecasted_dmg","TVR_causualities",
                      "TVR_traffic_jams","TVR_preparing","TVR_stay","TVR_evac",
                      "SM_dmg_done","SM_forecasted_dmg","SM_causualities",
                      "SM_traffic_jams","SM_preparing","SM_stay","SM_evac")
gen_bar_plot(pre_florence,category_to_plot)
```

### Ploting specific pre questions

```{r echo=FALSE}
#### list of things to plot
category_to_plot <- c("heard_florence","when_first_hear","official_notice",
                      "mandatory_evac_notice","voluntary_evac_notice",
                      "mandatory_stay_notice","voluntary_stay_notice")
gen_bar_plot(pre_florence,category_to_plot)
```

## Post Florence Plot
### Ploting demographical information 

```{r echo=FALSE}
## Standard Summarization of Categorical variables in barplot
#### list of things to plot
category_to_plot <- c("gender","num_vehicle","has_pet",
                      "child_0_5","child_6_12","child_13_18","elder_65_up",
                      "special_need_med","special_need_moving")
gen_bar_plot(post_florence,category_to_plot)
```
```{r echo=FALSE, fig.width=15}
category_to_plot <- c("edu","income","house_structure","years_in_resident",
                      "distance_to_coast")
gen_bar_plot(post_florence,category_to_plot)
```
```{r echo=FALSE}
## Standard summarization of numerical variables in boxplot
numerical_to_plot <- c("family_size")
gen_box_plot(post_florence,numerical_to_plot,15)
```

### Ploing social influence

```{r echo=FALSE, fig.width=10}
#### list of things to plot
category_to_plot <- c("contribute_final_decision","household_discussion","household_agreement",
                      "outside_family_discussion","outside_family_agreement",
                      "outside_friend_discussion","outside_friend_agreement",
                      "neighbors_observation","neighbors_agreement")
gen_bar_plot(post_florence,category_to_plot)
```

### Ploting previous experience

```{r echo=FALSE}
#### list of things to plot
category_to_plot <- c("prev_exp","prev_exp_decision")
gen_bar_plot(post_florence,category_to_plot)
```

### Ploting probability estimation 

```{r echo=FALSE, fig.width=14}
#### list of things to plot
category_to_plot <- c("safety_prob",
                      "flood_depth","electricity_lost_dur","normal_condition_return",
                      "hurricane_category")
gen_bar_plot(post_florence,category_to_plot)
```

### Ploting information

```{r echo=FALSE, fig.width=10}
#### list of things to plot
category_to_plot <- c("TVR_dmg_done","TVR_forecasted_dmg","TVR_causualities",
                      "TVR_traffic_jams","TVR_preparing","TVR_stay","TVR_evac",
                      "SM_dmg_done","SM_forecasted_dmg","SM_causualities",
                      "SM_traffic_jams","SM_preparing","SM_stay","SM_evac")
gen_bar_plot(post_florence,category_to_plot)
```

### First heard, official notice, and decision

```{r echo=FALSE}
#### list of things to plot
category_to_plot <- c("emergency_request_before","emergency_request_during",
                      "emergency_request_after","official_notice",
                      "mandatory_evac_notice","voluntary_evac_notice",
                      "mandatory_stay_notice","voluntary_stay_notice",
                      "evac_decision","same_choice")
gen_bar_plot(post_florence,category_to_plot)
```
```{r echo=FALSE, fig.width=16}
#### list of things to plot
category_to_plot <- c("notice_when")
gen_bar_plot(post_florence,category_to_plot)
```
```{r echo=FALSE}
#### list of things to plot
category_to_plot <- c("mandatory_evac_notice","voluntary_evac_notice",
                      "mandatory_stay_notice","voluntary_stay_notice",
                      "evac_decision","same_choice")
gen_bar_plot(post_florence,category_to_plot)
```


### Evac related questions

```{r echo=FALSE, fig.width=16}
#### list of things to plot
category_to_plot <- c("date_evac","time_evac","how_evac","where_evac",
                      "how_far_evac")
gen_bar_plot(post_florence,category_to_plot)
```
```{r echo=FALSE}
#### list of things to plot
numerical_to_plot <- c("traveling_cost_evac","place_cost_evac")
gen_box_plot(post_florence,numerical_to_plot,3000)
```

### Stay related questions

```{r echo=FALSE}
#### list of things to plot
category_to_plot <- c("prepare_stay")
gen_bar_plot(post_florence,category_to_plot)
```
```{r echo=FALSE, fig.width=16}
#### list of things to plot
category_to_plot <- c("when_prepare_stay","amount_prepare_stay")
gen_bar_plot(post_florence,category_to_plot)
```
```{r echo=FALSE}
#### list of things to plot
numerical_to_plot <- c("traveling_est_stay","place_cost_est_stay")
gen_box_plot(post_florence,numerical_to_plot,3000)
```
