---
title: "Basis Analysis of Post Hurricane Michael"
output: html_document
params:
  only_nc_sc: TRUE
---

```{r setup, include=FALSE}
options(width = 100)
```

```{r echo=FALSE, include=FALSE}
library(readr)
post_michael  <- read_csv("Data/pre-processed post michael.csv")
```

### Sample size

```{r}
dim(post_michael)[1]
```

## inclusion/exclusion cretiria
#### Only GA or FL
```{r}
table(post_michael$state)
```

```{r echo=FALSE, include=FALSE}
## Organize order of factor
gender_order <- c("Female","Male","Other")
post_michael$gender  <- factor(post_michael$gender, levels=gender_order)

edu_order <- c("Some high school","High school graduate",
               "Some college","College graduate","Graduate school")
post_michael$edu  <- factor(post_michael$edu, levels=edu_order)

employment_order <- c("Student","Employed part time","Employed full time","Unemployed looking for work",
                      "Unemployed not looking for work","Retired","Disabled")
post_michael$employment <- factor(post_michael$employment, levels=employment_order)

income_order <- c("Less than $20,000","$20,000 to $40,000","$40,000 to $60,000",
                  "$60,000 to $80,000","$80,000 to $100,000","$100,000 to $150,000",
                  "Over $150,000")
post_michael$income  <- factor(post_michael$income, levels=income_order)

house_order <- c("Mobile or  trailer home","Detached single family house","Duplex or triplex house","Condominium/apartment","Other")
post_michael$house_structure  <- factor(post_michael$house_structure, levels=house_order)

years_in_res_order <- c("Less than 1 year","1  - 3 years","3 - 5 years",
                        "5 - 10 years","More than 10 years")
post_michael$years_in_resident  <- factor(post_michael$years_in_resident, levels=years_in_res_order)

distance_order <- c("Within 1 mile","1 to 4 miles","4 to 10 miles",
                   "10 to 30 miles","30 to 50 miles","More than 50 miles")
post_michael$distance_to_coast  <- factor(post_michael$distance_to_coast, levels=distance_order)

num_vehicle_order <- c("None","One","More than one")
post_michael$num_vehicle  <- factor(post_michael$num_vehicle, levels=num_vehicle_order)

important_order <- c("Extremely important","Very important","Moderately important","Slightly important","Not at all important")
post_michael$importance_of_pet  <- factor(post_michael$importance_of_pet, levels=important_order)

amount_order <- c("None at all","A little","A moderate amount","A lot","A great deal")
suggestion_order <- c("Strongly suggested to evacuate","Suggested to evacuate","Did not make any suggestion","Suggested to stay","Strongly suggested to stay")

## social influence
post_michael$contribute_final_decision <- factor(post_michael$contribute_final_decision, levels=amount_order)
post_michael$household_discussion      <- factor(post_michael$household_discussion, levels=amount_order)
post_michael$outside_family_discussion <- factor(post_michael$outside_family_discussion, levels=amount_order)
post_michael$outside_friend_discussion <- factor(post_michael$outside_friend_discussion, levels=amount_order)
post_michael$neighbors_observation     <- factor(post_michael$neighbors_observation, levels=amount_order)

post_michael$household_suggestion      <- factor(post_michael$household_suggestion, levels=suggestion_order)
post_michael$outside_family_suggestion <- factor(post_michael$outside_family_suggestion, levels=suggestion_order)
post_michael$outside_friend_suggestion <- factor(post_michael$outside_friend_suggestion, levels=suggestion_order)
post_michael$neighbors_doing           <- factor(post_michael$neighbors_doing, levels=suggestion_order)

## infomation
post_michael$TVR_causualities   <- factor(post_michael$TVR_causualities, levels= amount_order)
post_michael$TVR_dmg_done       <- factor(post_michael$TVR_dmg_done, levels= amount_order)
post_michael$TVR_evac           <- factor(post_michael$TVR_evac, levels= amount_order)
post_michael$TVR_forecasted_dmg <- factor(post_michael$TVR_forecasted_dmg, levels= amount_order)
post_michael$TVR_preparing      <- factor(post_michael$TVR_preparing, levels= amount_order)
post_michael$TVR_stay           <- factor(post_michael$TVR_stay, levels= amount_order)
post_michael$TVR_traffic_jams   <- factor(post_michael$TVR_traffic_jams, levels= amount_order)
post_michael$SM_causualities    <- factor(post_michael$SM_causualities, levels= amount_order)
post_michael$SM_dmg_done        <- factor(post_michael$SM_dmg_done, levels= amount_order)
post_michael$SM_evac            <- factor(post_michael$SM_evac, levels= amount_order)
post_michael$SM_forecasted_dmg  <- factor(post_michael$SM_forecasted_dmg, levels= amount_order)
post_michael$SM_preparing       <- factor(post_michael$SM_preparing, levels= amount_order)
post_michael$SM_stay            <- factor(post_michael$SM_stay, levels= amount_order)
post_michael$SM_traffic_jams    <- factor(post_michael$SM_traffic_jams, levels= amount_order)

prob_order <- c("Extremely unlikely","Moderately unlikely","Slightly unlikely","Neither likely nor unlikely (50/50)","Slightly likely","Moderately likely","Extremely likely")
post_michael$safety_prob <- factor(post_michael$safety_prob, levels=prob_order)

flood_depth_order <- c("Will not be flooded","1 foot or less","1 - 3 feet","3 - 5 feet",
                       "More than 5 feet")
post_michael$flood_depth <- factor(post_michael$flood_depth, levels=flood_depth_order)

electricity_dur_order <- c("Will not lose electricity","Less than one week","1 - 2 weeks","2- 3 weeks","3 - 4 weeks","More than a month")
post_michael$electricity_lost_dur <- factor(post_michael$electricity_lost_dur, levels=electricity_dur_order)

normal_cond_order <- c("Less than one week","1 - 2 weeks","2 -3 weeks","3 -4 weeks","More than a month")
post_michael$normal_condition_return <- factor(post_michael$normal_condition_return, levels=normal_cond_order)

## notice type factor
post_michael$mandatory_evac_notice <- factor(post_michael$mandatory_evac_notice)
post_michael$voluntary_evac_notice <- factor(post_michael$voluntary_evac_notice)
post_michael$voluntary_stay_notice <- factor(post_michael$voluntary_stay_notice)
post_michael$mandatory_stay_notice <- factor(post_michael$mandatory_stay_notice)

## Date ordering
first_heard_order <- c("October 7th or before","October 8th","October 9th","October 10th")
post_michael$first_hear_florence <- factor(post_michael$first_hear_florence, levels = first_heard_order)

date_evac_order <- c("October 7th or before","October 8th","October 9th","October 10th","October 11th or after")
post_michael$date_evac <- factor(post_michael$date_evac, levels=date_evac_order)

when_prepare_stay_order <- c("October 7th or before","October 8th","October 9th","October 10th")
post_michael$when_prepare_stay <- factor(post_michael$when_prepare_stay, levels=when_prepare_stay_order)

## Other don't care about order but need to translate it to factor for summarization purpose
all_character_class_post <- names(post_michael[,sapply(post_michael,is.character)])
for(name in all_character_class_post)
{
  post_michael[[name]] <- as.factor(post_michael[[name]])
}

```

# Standard summarization in text 

## Demographical Infomation

```{r}
summary(post_michael[6:27])
```

## Social influence

```{r}
summary(post_michael[28:36])
```

## Prev experience

```{r}
summary(post_michael[36:42])
```

## Probability and Estimation

```{r}
summary(post_michael[43:49])
```

## Infomation

```{r}
summary(post_michael[50:65])
```

## First hear, Official Notice, emergency request and decision

```{r}
summary(post_michael[66:74])
```

## Evac specific question

```{r}
summary(post_michael[75:83])
```

## Stay specific question

```{r}
summary(post_michael[84:88])
```

## Notice type specific question

```{r}
summary(post_michael[89:92])
```

#### Correlation Table

```{r echo=FALSE}
y_list <- c("flood_cost","electricity_cost",
            "traveling_cost","safe_place_cost","safety_prob",
            "flood_depth","electricity_lost_dur","normal_condition_return","evac_decision_num")

x_list <- c("age","gender","edu","income","house_structure","years_in_resident","distance_to_coast","num_vehicle",
            "has_pet","family_size","child_0_5","child_6_12","child_13_18","elder_65_up",
             "special_need_med","special_need_moving",
             "mandatory_evac_notice","voluntary_evac_notice","prev_exp_decision",
            "flood_cost","electricity_cost",
            "traveling_cost","safe_place_cost","safety_prob",
            "flood_depth","electricity_lost_dur","normal_condition_return")
## Clearning up some features
post_michael$evac_decision_num <- as.numeric(post_michael$evac_decision)
post_michael$prev_exp_decision <- ifelse(post_michael$prev_exp == "No",0, ifelse(post_michael$prev_exp_decision == "Evacuated",1,2))

post_michael$traveling_cost <- ifelse(post_michael$evac_decision == "No", post_michael$traveling_est_stay, post_michael$traveling_cost_evac)
post_michael$safe_place_cost <- ifelse(post_michael$evac_decision == "No", post_michael$place_cost_est_stay, post_michael$place_cost_evac)

dat <- post_michael

for(x in x_list)
{
  temp <- ""
  for(y in y_list)
  {
    cor_temp <- round(cor(as.numeric(dat[[x]]),as.numeric(dat[[y]])),digits=2)
    temp <- paste(temp,cor_temp, sep=" & ")
  }
  print(x)
  print(temp)
}

```

```{r echo=FALSE}
## helper function for ploting
gen_bar_plot <- function(dat,plot_list)
{
  for(i in plot_list)
  {
    barplot(table(dat[[i]]),ylab="Number of response",xlab=i)
  }
}
gen_box_plot <- function(dat,plot_list,maxy)
{
  for(i in plot_list)
  {
    boxplot(dat[[i]],ylab="value (count or cost)",xlab=i,ylim=c(0,maxy))
  }
}

```

## Post Michael Plot
### Ploting demographical information 

```{r echo=FALSE}
## Standard Summarization of Categorical variables in barplot
#### list of things to plot
category_to_plot <- c("gender","num_vehicle","has_pet",
                      "child_0_5","child_6_12","child_13_18","elder_65_up",
                      "special_need_med","special_need_moving")
gen_bar_plot(post_michael,category_to_plot)
```
```{r echo=FALSE, fig.width=15}
category_to_plot <- c("edu","income","house_structure","years_in_resident",
                      "distance_to_coast")
gen_bar_plot(post_michael,category_to_plot)
```
```{r echo=FALSE}
## Standard summarization of numerical variables in boxplot
numerical_to_plot <- c("family_size")
gen_box_plot(post_michael,numerical_to_plot,15)
```

### Ploing social influence

```{r echo=FALSE, fig.width=10}
#### list of things to plot
category_to_plot <- c("contribute_final_decision","household_discussion","household_suggestion",
                      "outside_family_discussion","outside_family_suggestion",
                      "outside_friend_discussion","outside_friend_suggestion",
                      "neighbors_observation","neighbors_doing")
gen_bar_plot(post_michael,category_to_plot)
```

### Ploting previous experience

```{r echo=FALSE}
#### list of things to plot
category_to_plot <- c("prev_exp","prev_exp_decision")
gen_bar_plot(post_michael,category_to_plot)
```

### Ploting probability estimation 

```{r echo=FALSE, fig.width=14}
#### list of things to plot
category_to_plot <- c("safety_prob",
                      "flood_depth","electricity_lost_dur","normal_condition_return",
                      "hurricane_category")
gen_bar_plot(post_michael,category_to_plot)
```

### Ploting information

```{r echo=FALSE, fig.width=10}
#### list of things to plot
category_to_plot <- c("TVR_dmg_done","TVR_forecasted_dmg","TVR_causualities",
                      "TVR_traffic_jams","TVR_preparing","TVR_stay","TVR_evac",
                      "SM_dmg_done","SM_forecasted_dmg","SM_causualities",
                      "SM_traffic_jams","SM_preparing","SM_stay","SM_evac")
gen_bar_plot(post_michael,category_to_plot)
```
```{r echo=FALSE}  
numerical_to_plot <- c("flood_cost","electricity_cost")
gen_box_plot(post_michael,numerical_to_plot,3000)
```

### First heard, official notice, and decision

```{r echo=FALSE}
#### list of things to plot
category_to_plot <- c("emergency_request_before","emergency_request_during",
                      "emergency_request_after","official_notice",
                      "mandatory_evac_notice","voluntary_evac_notice",
                      "mandatory_stay_notice","voluntary_stay_notice",
                      "evac_decision","same_choice")
gen_bar_plot(post_michael,category_to_plot)
```
```{r echo=FALSE, fig.width=16}
#### list of things to plot
category_to_plot <- c("notice_when")
gen_bar_plot(post_michael,category_to_plot)
```
```{r echo=FALSE}
#### list of things to plot
category_to_plot <- c("mandatory_evac_notice","voluntary_evac_notice",
                      "mandatory_stay_notice","voluntary_stay_notice",
                      "evac_decision","same_choice")
gen_bar_plot(post_michael,category_to_plot)
```


### Evac related questions

```{r echo=FALSE, fig.width=16}
#### list of things to plot
category_to_plot <- c("date_evac","time_evac","how_evac","where_evac",
                      "how_far_evac")
gen_bar_plot(post_michael,category_to_plot)
```
```{r echo=FALSE}
#### list of things to plot
numerical_to_plot <- c("traveling_cost_evac","place_cost_evac")
gen_box_plot(post_michael,numerical_to_plot,3000)
```

### Stay related questions

```{r echo=FALSE}
#### list of things to plot
category_to_plot <- c("prepare_stay")
gen_bar_plot(post_michael,category_to_plot)
```
```{r echo=FALSE, fig.width=16}
#### list of things to plot
category_to_plot <- c("when_prepare_stay","amount_prepare_stay")
gen_bar_plot(post_michael,category_to_plot)
```
```{r echo=FALSE}
#### list of things to plot
numerical_to_plot <- c("traveling_est_stay","place_cost_est_stay")
gen_box_plot(post_michael,numerical_to_plot,3000)
```
